---
title: "Core Concepts of rg2(G2)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Core Concepts of rg2(G2)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

rg2 is a G2 binding for R

[Core Concepts of G2](https://g2.antv.antgroup.com/en/manual/core/chart)


```{r}
library(rg2)
g2(iris, encode('Sepal.Length','Sepal.Width',color='Species', shape='point',size=5)) + g2_point()
```


**可以同时在view/mark配置的属性需要分别在g2/g2_xxx进行支持**

- Mark mark is used as the basic visual component unit
- View view is used to draw multiple marks. A view has a coordinate system and is the smallest unit of application interaction.
- Composite composition provides the ability to draw multiple charts in a single visualization

compare view and Composite in Spec:

```js
/*
 options:
 - type: view <=> spaceLayer/spaceFlex/facetCircle/facetRect/repeatMatrix
 - children: array of marks
 - encode:
  - view: YES
  - facetCircle: YES
  - facetRect: YES
  - repeatMatrix: YES
  - spaceLayer: NO
  - spaceFlex: NO
  
 encode will be passed to every mark if mark has no encode,
 and mark.encode has a higher priority?
*/
{
  type: '...',
  children: [{type: 'line'}, {type:'point'}]
}

```

```js
/*
 view
 view's encode will be passed to every mark if mark has no encode.
 
*/

{
  type: 'view',
  encode: {},
  children: [{type: 'line'}, {type:'point'}]
}

/*
 composite
 
 */
{
  type: '...',
  [encode: {},]
  children: [{type: 'line'}, {type:'point'}]
}
```
## View Tree

Overall, G2's spec is a hierarchical **view tree**, composed of different nodes. Nodes specify their types through `node.type`, different types have different functions, and they are nested through `node.children`.
```
{
  type: 'spaceFlex',
  children: [
    {
      type: 'view',
      children: [{ type: 'line' }, { type: 'point' }],
    },
    {
      type: 'interval',
    },
  ],
}
```
The view can be simply understood as a chart, or `a single view plot`. This "tree" manages views in time and space through different container nodes, thereby managing our views in time and space to draw `multiple view plots`.


There are three types of nodes in G2.

- Mark nodes
- View nodes
- Composite nodes

### Mark

Mark nodes are leaf nodes on this tree, which cannot be nested further, that is, they cannot contain the children attribute. Marks are similar to the concept of a chart. For example, an Interval mark can draw a bar chart.

```
{
  type: 'interval',
  ...
}
```


### View

If you want to have multiple marks in the chart, you need to put them into view nodes to draw a single view plot. View nodes can only nest mark nodes.

```
{
  type: 'view',
  children: [{ type: 'line' }, { type: 'point' }],
}
```


### Composition

Composition is used to draw multiple views in a chart (multi-view chart). It can nest composite nodes, view nodes and mark nodes.

```js
{
  type: 'spaceFlex',
  children: [
    { type: 'spaceFlex' }, // composition node
    { type: 'view' },      // view node
    { type: 'interval' },  // mark node
  ],
}
```


`View Composition` in G2 provides the ability to draw multiple charts in a single visualization.G2 defines a `View Graph` to describe a `Multi-View Plot`.



**`g2()` is used to generate basic option of G2**

---

## Mark

There is **no concept of chart** in G2, but the mark is used as the basic visual component unit. Any chart is composed of multiple marks. Unlike traditional drawing systems, marks provide the ability to draw abstract data.


```r
# no plot, just generate a basic mark option
p = g2(mtcars, encode('mpg', 'disp'))
p

# point plot
g2(mtcars, encode('mpg', 'disp')) + g2_point()
```

Mark can also be placed inside a view and add multiple marks to the view:
```
g2_view(mtcars, encode('mpg', 'disp')) + g2_point() + g2_line()
```

Marks are the "first-class citizens" in G2: the most important concept in G2, a mark is composed of the following core concepts:

- data - visual data
- encode - encoding information
- scale - mapping rules
- transform - transformation channel values
- layout - configuration of layout algorithms
- coordinate - transformation of coordinate systems
- style - visual styles
- viewStyle - visual styles of the view
- animate - animation properties
- state - style of state
- label - data labels
- title - chart title
- axis - coordinate axes
- legend - legend
- tooltip - prompt information
- scrollbar - scrollbar
- slider - drag axis
- interaction - interaction
- theme - theme

```js
g2(data, encode(...)) + g2_point() + scale() + ...
```

**`g2_` family**

- g2_point()
- g2_line() 


